Output Summary

### 2023-03-31 03-post-process/output-plots-children/02-mcmc-diags.Rmd
Update MCMC diagnostic text

* $\boldsymbol{\hat{R}}$ measures convergence of multiple chains to a common target distribution. Values close to 1 are ideal, greater than 1.1 are problematic but possibly passable, and greater than 1.2 should probably not be used for inference (general rules).
* **ESS** measures the number of effective MCMC samples are available to estimate a given summary statistic of the posterior -- here the posterior mean and quantiles of the 95% equal-tailed CRI. Percentages shown represent the fraction of parameters that have fewer than 400 ESS -- which Vehtari et al. [2021](https://projecteuclid.org/journals/bayesian-analysis/advance-publication/Rank-Normalization-Folding-and-Localization--An-Improved-R%cb%86-for/10.1214/20-BA1221.full) suggest as a good rule of thumb.
* **MCCV** is Monte Carlo Standard Error of a summary statistic divided by the estimated posterior summary statistic, intended to represent a measure of precision for estimating posterior summary statistics -- here the posterior mean and quantiles of the 95% equal-tailed CRI. Percentages shown represent the fraction of parameters that have greater than 5% MCCV -- which Staton has (arbitrarily and at this time) chosen as the greatest amount of acceptable imprecision.

>>>>

* $\boldsymbol{\hat{R}}$ measures convergence of multiple chains to a common target distribution. Values close to 1 are ideal but values greater than 1.2 should be considered not well-converged (general rules of thumb).
* **ESS** measures the number of effective MCMC samples are available to estimate a given summary statistic of the posterior -- here the posterior mean and quantiles of the 95% equal-tailed CRI. Percentages shown represent the fraction of parameters that have fewer than 400 ESS -- Vehtari et al. [2021](https://projecteuclid.org/journals/bayesian-analysis/advance-publication/Rank-Normalization-Folding-and-Localization--An-Improved-R%cb%86-for/10.1214/20-BA1221.full) suggests 400 as a good rule of thumb.
* **MCCV** is Monte Carlo Standard Error of a summary statistic divided by the estimated posterior summary statistic, intended to represent a measure of precision for estimating posterior summary statistics -- here the posterior mean and quantiles of the 95% equal-tailed CRI. Percentages shown represent the fraction of parameters that have greater than 5% MCCV -- which Staton has deemed an acceptable level of imprecision.
